\documentclass[11pt,a4paper]{moderncv}

\moderncvstyle{classic}
\moderncvcolor{blue}
\nopagenumbers{}

% character encoding
\usepackage[utf8]{inputenc}
\usepackage{fontawesome}
\usepackage{tabularx}
\usepackage{ragged2e}

\usepackage[scale=0.8]{geometry}
 \geometry{
 a4paper,
 total={170mm,257mm},
 left=7mm,
 right=7mm,
 top=5mm,
 bottom=5mm
 }
\usepackage{multicol}
\usepackage{import}

\name{Andrey}{Zvonov}

\firstname{Andrey}
\familyname{Zvonov}
\address{Roermond, Netherlands}{}


\newcommand*{\customcventry}[7][.30em]{
  \begin{tabular}{@{}l}
    {\bfseries #4}
  \end{tabular}
  \hfill% move it to the right
  \begin{tabular}{l@{}}
     {\bfseries #5}
  \end{tabular} \\
  \begin{tabular}{@{}l}
    {\itshape #3}
  \end{tabular}
  \hfill% move it to the right
  \begin{tabular}{l@{}}
     {\itshape #2}
  \end{tabular}
  \ifx&#7&%
  \else{\\%
    \begin{minipage}{\maincolumnwidth}%
      \small#7%
    \end{minipage}}\fi%
  \par\addvspace{#1}}

\setlength{\tabcolsep}{10pt}

\begin{document}
\makecvtitle
\vspace*{-12mm}


\begin{center}
\begin{tabular}{ c c c c }
 \faEnvelopeO\href{mailto:zvonov.andrey@gmail.com}{ zvonov.andrey@gmail.com} & \faLinkedin\href{https://linkedin.com/in/zvonand}{ zvonand} & \faGithub\href{https://github.com/zvonand}{ github.com/zvonand}
\end{tabular}
\end{center}

% \vspace*{1mm}



\section{About Me}{
I am a Software Engineer with a strong proficiency in Python and C++, and a modest yet valuable experience in Java.
        
Currently, I work at Altinity, Inc. in a diverse and globally distributed team, and actively contribute to the development of ClickHouse.

My B.Sc. in Applied Mathematics and Computer Science from Lomonosov Moscow State University equipped me with robust skills in computer science (algorithms, data structures, etc.) and mathematics.

Alongside my studies and professional role, I've served as a Teaching Assistant for the Computer Networks course at Moscow Institute of Physics and Technology, refining my communication and mentorship skills.

Also, I am authorized to work in the Netherlands as a highly skilled migrant (kennismigrant).
}

\section{Professional Experience}

\customcventry{NL}{Software Engineer, Software Engineer in QA}{Altinity, Inc.}{Sep 2020 -- Current}{}{\begin{itemize}
    \item Enhancing ClickHouse:
    \begin{itemize}
        \item Delivered a number of new features and improvements,
        \item Co-authored and updated multiple sections of end-user documentation;
    \end{itemize}
    \item Maintained the GitLab CI/CD infrastructure and pipeline for releasing \textit{Altinity Stable} ClickHouse builds.
    \item Designed and enhanced automated tests for:
    \begin{itemize}
        \item A number of ClickHouse features,
        \item Altinity ClickHouse Backup utility,
        \item Altinity.Cloud DBaaS platform API,
    \end{itemize}
\end{itemize}}
\ \newline
\customcventry{RU}{Intern Software Engineer}{Applied Research Center for Computer Networks}{Nov 2019 -- Aug 2020}{}{
    \begin{itemize}
        % \setlength{\itemsep}{-3pt}
        \item Contributed to the development of RUNOS SDN controller,
        \item Collaborated in a team of three to design and develop a QoS tunnel management application using NETCONF.
    \end{itemize}
}

\section{Skills}
   	\begin{itemize}
         \item C++, Python, Java;
         \item Bash, SQL
         \item Linux, Docker, CI/CD, Git;
	\end{itemize}

\section{Education}

{\customcventry{RU}{B.Sc.}{Lomonosov Moscow State University (MSU)}{Sep 2017 -- Aug 2022}{}{Applied Mathematics and Computer Science}

{\begin{itemize}
    \item Cumulative GPA -- \textbf{4.4/5},
    \item Minor: Distributed Systems and Networks,
    \item Bachelor's thesis: \textit{On efficiency analysis of multipath routing algorithms}.
  \end{itemize}}
}

\section{MOOC \& Courses}
\begin{multicols}{2}
\begin{itemize}
    \item Formal methods of software design and verification (Sirius University, Nov 2021)
    \item Introduction to C++: White Belt (Coursera)
    \vfill\null
    \columnbreak
    \item Build a Modern Computer from First Principles: From Nand to Tetris (Coursera)
    \item  Kubernetes for the Absolute Beginners (Udemy)
\end{itemize}
\end{multicols}


\section{Languages}
{\begin{multicols}{3}
\textbf{Russian} -- Native

\textbf{English} -- C1 (IELTS certified)

\textbf{German} -- Basic

\end{multicols}
}


\end{document}

