\documentclass[11pt,a4paper,roman]{moderncv}

\moderncvstyle{classic}


\moderncvcolor{blue}

\nopagenumbers{}

% character encoding
\usepackage[utf8]{inputenc}
\usepackage{fontawesome}
\usepackage{tabularx}
\usepackage{ragged2e}

\usepackage[scale=0.8]{geometry}
 \geometry{
 a4paper,
 total={170mm,257mm},
 left=7mm,
 right=7mm,
 top=5mm,
 bottom=5mm
 }
\usepackage{multicol}

\usepackage{import}

\name{Andrey}{Zvonov}


\newcommand*{\customcventry}[7][.30em]{
  \begin{tabular}{@{}l}
    {\bfseries #4}
  \end{tabular}
  \hfill% move it to the right
  \begin{tabular}{l@{}}
     {\bfseries #5}
  \end{tabular} \\
  \begin{tabular}{@{}l}
    {\itshape #3}
  \end{tabular}
  \hfill% move it to the right
  \begin{tabular}{l@{}}
     {\itshape #2}
  \end{tabular}
  \ifx&#7&%
  \else{\\%
    \begin{minipage}{\maincolumnwidth}%
      \small#7%
    \end{minipage}}\fi%
  \par\addvspace{#1}}


\setlength{\tabcolsep}{10pt}

\begin{document}
\makecvtitle
\vspace*{-12mm}


\begin{center}
\begin{tabular}{ c c c }
 \faEnvelopeO\enspace zvonov.andrey@gmail.com & \faMobile\enspace +7 (916) 396-02-50 & \faLinkedin\enspace linkedin.com/zvonand
\end{tabular}
\end{center}

\vspace*{2mm}



\section{About Me}{
 {\begin{itemize}
    \item Pursuing Bachelor's degree at Lomonosov Moscow State University, Faculty of Computational Mathematics and Cybernetics.
    \item Teaching Assistant at Computer Networks course in Moscow Institute of Physics and Technology.
    \item QA Engineer at Altinity, Inc.

  \end{itemize}
}
}

\section{Professional Experience}

\customcventry{Remote}{Software Engineer in QA}{Altinity, Inc.}{Sep 2020 -- Present}{}{Create automated tests for a number of features in \textbf{ClickHouse} and utilites, such as \textit{ClickHouse Backup}, \textit{ClickHouse Operator}, as well as our own cloud platform, \textit{Altinity.Cloud}. Contribute to ClickHouse --- improved DateTime64 data type handling, developed specific window functions. Maintain internal test\&build pipeline providing our clients with approved stable builds with a number of customizations.}

\customcventry{Moscow, Russia}{Intern Software Engineer}{Applied Research Center for Computer Networks}{Nov 2019 -- Aug 2020}{}{Participated in development of \textit{RUNOS} SDN controller --- developed a prototype of QoS application to manage tunnel creation via NETCONF.}

\section{Skills}
   	\begin{itemize}
         \item Python, C++, Git/GitLab/GitHub, SQL
         \item Linux, LaTeX, MATLAB/OCTAVE
	\end{itemize}

\section{Education}

{\customcventry{Moscow, Russia}{Bachelor studies}{Lomonosov Moscow State University}{Sep 2017 -- Present}{}{Distributed Systems and Computer Networks}

{\begin{itemize}
    \item Cumulative GPA -- \textbf{4.45/5}
    \item "Excellent" in Algorithms, Computer Networks, Assembly Language \& Computer Architecture, Operating Systems, Distributed Systems, Computations Scheduling in Distributed Systems.
  \end{itemize}}
}

\section{MOOC \& Courses}
\begin{itemize}
    \item Formal methods of software design and verification (Sirius University, Nov 2021)
    \item Introduction to HTML5, Introduction to CSS3, Interactivity with JavaScript (Coursera)
    \item Geometric Algorithms (Coursera)
    \item Introduction to C++: White Belt (Coursera) (in Russian)
    \item Build a Modern Computer from First Principles: From Nand to Tetris (Coursera)
    \item An Introduction to Interactive Programming in Python (Coursera)
    \item Developing Android Apps (Udacity)
\end{itemize}


\section{Research}
  {\begin{itemize}
   \item \textbf{On routing of demultiplexed connections with considering current network state.}\\
   (3rd year coursework). An algorithm finding a set of routes corresponding to a given request was proposed and its test was performed using network topologies from TopologyZoo.

   \item \textbf{On efficiency analysis of multipath routing algorithms.}\\
   (Bachelor's thesis, in progress). The goal of the thesis is to analyse efficiency of a number of algorithms finding a set of routes in a given topology applied to particular tasks.
 \end{itemize}
}


\section{Languages}
{\begin{multicols}{3}
\textbf{Russian} -- \textit{native}

\textbf{English} -- \textit{fluent}

\textbf{German} -- \textit{basic}

\end{multicols}
}


\end{document}
