\documentclass[11pt,a4paper]{moderncv}

\moderncvstyle{classic}
\moderncvcolor{red}
\nopagenumbers{}

% character encoding
\usepackage[utf8]{inputenc}
\usepackage{fontawesome}
\usepackage{tabularx}
\usepackage{ragged2e}

\usepackage[scale=0.8]{geometry}
 \geometry{
 a4paper,
 total={170mm,257mm},
 left=7mm,
 right=7mm,
 top=5mm,
 bottom=5mm
 }
\usepackage{multicol}
\usepackage{import}

\name{Andrey}{Zvonov}


\newcommand*{\customcventry}[7][.30em]{
  \begin{tabular}{@{}l}
    {\bfseries #4}
  \end{tabular}
  \hfill% move it to the right
  \begin{tabular}{l@{}}
     {\bfseries #5}
  \end{tabular} \\
  \begin{tabular}{@{}l}
    {\itshape #3}
  \end{tabular}
  \hfill% move it to the right
  \begin{tabular}{l@{}}
     {\itshape #2}
  \end{tabular}
  \ifx&#7&%
  \else{\\%
    \begin{minipage}{\maincolumnwidth}%
      \small#7%
    \end{minipage}}\fi%
  \par\addvspace{#1}}


\setlength{\tabcolsep}{10pt}

\begin{document}
\makecvtitle
\vspace*{-12mm}


\begin{center}
\begin{tabular}{ c c c c }
 \faEnvelopeO\enspace zvonov.andrey@gmail.com & \faMobile\enspace +7 (916) 396-02-50 & \faLinkedin\enspace linkedin.com/in/zvonand & \faGithub\enspace github.com/zvonand
\end{tabular}
\end{center}

\vspace*{2mm}



\section{About Me}{
  \begin{itemize}
    \item B.Sc. in Applied Mathematics and CS at Lomonosov Moscow State University, Faculty of Computational Mathematics and Cybernetics.
    \item Software Engineer in QA at Altinity, Inc.
    \item Teaching Assistant at Computer Networks course in Moscow Institute of Physics and Technology.
  \end{itemize}
}

\section{Professional Experience}

\customcventry{Remote}{Software Engineer}{Altinity, Inc.}{June 2020 -- Present}{}{\begin{itemize}
    \item Enhancing ClickHouse DBMS: improved arithmetics and working with dates and times, added some (window) functions, introduced a number of small fixes.
\end{itemize}}

\customcventry{Remote}{Software Engineer in QA}{Altinity, Inc.}{Sep 2020 -- May 2022}{}{\begin{itemize}
    \item Developed and improved automated tests for a number of features in \textit{ClickHouse} and utilites, such as \textit{Altinity ClickHouse Backup}, \textit{Altinity ClickHouse Operator} and for \textit{Altinity.Cloud} platform API,
    \item Maintained internal test\&build pipeline,
    \item Contributed to \textit{ClickHouse}.
\end{itemize}}

\customcventry{Moscow, Russia}{Intern Software Engineer}{Applied Research Center for Computer Networks}{Nov 2019 -- Aug 2020}{}{\begin{itemize}
    \item Participated in general development of \textit{RUNOS} SDN controller,
    \item Was part of team developing a QoS tunnel management application via NETCONF.
\end{itemize}}

\section{Skills}
   	\begin{itemize}
         \item Python, C++, Git/GitLab/GitHub, SQL, Databases
         \item Linux, LaTeX.
	\end{itemize}

\section{Education}

{\customcventry{Moscow, Russia}{B.Sc.}{Lomonosov Moscow State University}{Sep 2017 -- Jun 2022}{}{Distributed Systems and Computer Networks}

{\begin{itemize}
    \item Cumulative GPA -- \textbf{4.4/5}
    \item "Excellent" in Algorithms, Operating Systems, Computer Networks, Assembly Language \& Computer Architecture, Distributed Systems, Computations Scheduling in Distributed Systems.
    \item \textbf{Coursework}: \textit{On routing of demultiplexed connections with considering current network state}.\\
    Proposed an algorithm finding a set of routes satisfying a given bandwidth request, performed its efficiency analysis.
    \item \textbf{Bachelor's thesis}: \textit{On efficiency analysis of multipath routing algorithms}.\\
    Performed efficiency analysis of some algorithms finding a set of routes satisfying a given request.
  \end{itemize}}
}

\section{MOOC \& Courses}
\begin{multicols}{3}
\begin{itemize}
    \item Formal methods of software design and verification (Sirius University, Nov 2021)
    \item Introduction to HTML5, Introduction to CSS3, Interactivity with JavaScript (Coursera)
    \item Geometric Algorithms (Coursera)
    \item Introduction to C++: White Belt (Coursera) (in Russian)
    \item Build a Modern Computer from First Principles: From Nand to Tetris (Coursera)
    \item An Introduction to Interactive Programming in Python (Coursera)
    \item Developing Android Apps (Udacity)
\end{itemize}
\end{multicols}


\section{Languages}
{\begin{multicols}{3}
\textbf{Russian} -- Native

\textbf{English} -- C1 (IELTS certificate present)

\textbf{German} -- Basic

\end{multicols}
}


\end{document}
