\documentclass[11pt,a4paper]{moderncv}

\moderncvstyle{classic}
\moderncvcolor{blue}
\nopagenumbers{}

% character encoding
\usepackage[utf8]{inputenc}
\usepackage{fontawesome}
\usepackage{tabularx}
\usepackage{ragged2e}

\usepackage[scale=0.8]{geometry}
 \geometry{
 a4paper,
 total={170mm,257mm},
 left=7mm,
 right=7mm,
 top=5mm,
 bottom=5mm
 }
\usepackage{multicol}
\usepackage{import}

\name{Andrey}{Zvonov}


\newcommand*{\customcventry}[7][.30em]{
  \begin{tabular}{@{}l}
    {\bfseries #4}
  \end{tabular}
  \hfill% move it to the right
  \begin{tabular}{l@{}}
     {\bfseries #5}
  \end{tabular} \\
  \begin{tabular}{@{}l}
    {\itshape #3}
  \end{tabular}
  \hfill% move it to the right
  \begin{tabular}{l@{}}
     {\itshape #2}
  \end{tabular}
  \ifx&#7&%
  \else{\\%
    \begin{minipage}{\maincolumnwidth}%
      \small#7%
    \end{minipage}}\fi%
  \par\addvspace{#1}}


\setlength{\tabcolsep}{10pt}

\begin{document}
\makecvtitle
\vspace*{-12mm}


\begin{center}
\begin{tabular}{ c c c c }
 \faEnvelopeO\enspace zvonov.andrey@gmail.com & \faLinkedin\enspace linkedin.com/in/zvonand & \faGithub\enspace github.com/zvonand
\end{tabular}
\end{center}

\vspace*{2mm}



\section{About Me}{
  \begin{itemize}
    \item B.Sc. in Applied Mathematics and CS at Lomonosov Moscow State University,
    \item Pursuing M.Sc. in high-load distributed systems at Moscow Institute of Physics and Technology,
    \item Software Engineer at Altinity, Inc,
    \item Teaching Assistant at Computer Networks course in Moscow Institute of Physics and Technology.
  \end{itemize}
}

\section{Professional Experience}

\customcventry{Remote}{Software Engineer}{Altinity, Inc.}{June 2020 -- Present}{}{\begin{itemize}
    \item Enhancing \textit{ClickHouse}: improved arithmetics and working with dates and times, added some (window) functions, introduced a number of fixes,
    \item Maintaining internal test\&build pipeline,
\end{itemize}}

\customcventry{Remote}{Software Engineer in QA}{Altinity, Inc.}{Sep 2020 -- May 2022}{}{\begin{itemize}
    \item Developed and improved automated tests for a number of features in \textit{ClickHouse} and utilites, such as \textit{Altinity ClickHouse Backup}, \textit{Altinity ClickHouse Operator} and for \textit{Altinity.Cloud} platform API,
    \item Maintained internal test\&build pipeline,
    \item Contributed to \textit{ClickHouse}.
\end{itemize}}

\customcventry{Moscow, Russia}{Intern Software Engineer}{Applied Research Center for Computer Networks}{Nov 2019 -- Aug 2020}{}{\begin{itemize}
    \item Participated in general development of \textit{RUNOS} SDN controller,
    \item Was part of team developing a QoS tunnel management application via NETCONF.
\end{itemize}}

\section{Skills}
   	\begin{itemize}
         \item C++, Python, Java;
         \item Linux, Git/GitLab/GitHub, SQL;
         \item HTML/JS (basic), \LaTeX.
	\end{itemize}

\section{Education}

{\customcventry{Moscow, Russia}{M.Sc.}{Moscow Institute of Physics and Technology (MIPT)}{Sep 2022 -- present}{}{Highloaded Distributed Systems}
}

{\customcventry{Moscow, Russia}{B.Sc.}{Lomonosov Moscow State University (MSU)}{Sep 2017 -- Aug 2022}{}{Distributed Systems and Computer Networks}

{\begin{itemize}
    \item Cumulative GPA -- \textbf{4.4/5}
    \item "Excellent" in Algorithms, Operating Systems, Computer Networks, Assembly Language \& Computer Architecture, Distributed Systems.
  \end{itemize}}
}

\section{MOOC \& Courses}
\begin{multicols}{2}
\begin{itemize}
    \item Formal methods of software design and verification (Sirius University, Nov 2021)
    \item Introduction to HTML5, Introduction to CSS3, Interactivity with JavaScript (Coursera)
    \vfill\null
    \columnbreak
    \item Introduction to C++: White Belt (Coursera)
    \item Build a Modern Computer from First Principles: From Nand to Tetris (Coursera)
    \item Developing Android Apps (Udacity)
\end{itemize}
\end{multicols}


\section{Languages}
{\begin{multicols}{3}
\textbf{Russian} -- Native

\textbf{English} -- C1 (IELTS ceritfied)

\textbf{German} -- Basic

\end{multicols}
}


\end{document}

